---
title: "Two Rate Proprioception Paper"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

# Overview

We have previously found that proprioception recalibrates within 6 trials, whereas visuomotor adaptation takes longer to saturate [@Ruttle2016; @Ruttle2018].

In this project we set out to investigate 1) exactly how quickly proprioception recalibrates, 2) to disentangle it from the updating of predicted sensory consequences, and 3) to see if it matches implicit learning that should follow the slow process [@McDougle2015] in the two-rate model [@Smith2006].

## Trial types

To do all this we use a trial-by-trial approach, that is: one reach-training trial is followed by one of various "measurement" trials: passive localization, active localization or no-cursor reaches (all of them explained below). As a control we also had people pause for a short bit instead. There were four groups of participants and each did one of the four "measurement" trials exclusively. With one exception, the pause and no-cursor group also did a set of localization trials before and after the regular paradigm also done by the other groups.

The first of each pair of trials is always one of these, both appear for every participant:
- reach training
- error-clamp

The second of each pair of trials is then one of these:
- passive localization (only proprioception)
- active localization (proprioception + prediction)
- no-cursor reach (classic measure of motor learning)
- pause (control)

These four trial types define the four paradigms, that is, each of the participants in the four groups only get 1 of these trial types throughout. However, the no-cursor group and pause group do get some passive localization before training, and after completion of the whole paradigm.

By comparing the trial-by-trial changes in the four paradigms, we can investigate the time-course of all these processes in more detail than we previously have.

## Figures

Preparing Data for Figures and Analysis:
```{r}
source('R/Analysis_Scripts.R')
source('R/Plots.R', encoding = 'UTF-8')
source('R/Repeated_Measures_Combine.R')
source('R/shared.R')
library('ez')
library('RateRate')
library('svglite')
library('effsize')
library('SMCL')
source('R/movement_times.R')
source('R/asymptoticDecayModel.R')
loadcolors()
downloadOSFdata()
loadalldata()
fixnocursorcolnames()
```
#Exploratory Figures
Individual Data 
```{r}
PlotIndividualdata(pause_reaches[33:320,],3, "Individual Pause Data", "Hand Direction [°]")
PlotIndividualdata(active_reaches,1, "Individual Active Data", "Hand Direction [°]")
PlotIndividualdata(passive_reaches,2, "Individual Passive Data", "Hand Direction [°]")
PlotIndividualdata(nocursor_reaches[33:320,],8, "Individual No-Cursor Data", "Hand Direction [°]")
PlotIndividualdata(nocursorI_reaches[33:320,],7, "Individual No-Cursor_I Data", "Hand Direction [°]")
PlotIndividualdata(newnocursor_reaches[33:320,],4, "Individual Combined No-Cursor Data", "Hand Direction [°]")
```

#Comparing the no-cursor test trials
```{r}
Plotnocursors(active_reaches, nocursor_nocursors, nocursorI_nocursors) 
ANOVAdata<- PrepdataforANOVA1(active_reaches, passive_reaches, pause_reaches[33:320,], nocursor_reaches[33:320,],nocursor_nocursors,nocursorI_reaches[33:320,],nocursorI_nocursors)

FullI1LANOVA<-ANOVAanalysis(ANOVAdata[ANOVAdata$Experiment == 'No-Cursor' | ANOVAdata$Experiment == 'No-CursorI' ,])
FullI1LANOVA

#FullNCANOVA<-ANOVAanalysis(ANOVAdata[ANOVAdata$Experiment == 'No-Cursor_No-Cursors' | ANOVAdata$Experiment == 'No-CursorI_No-Cursors',])
#FullNCANOVA
```


#Averaged reaches
```{r}
PlotallreachesCI(active_reaches,passive_reaches, pause_reaches[33:320,],newnocursor_reaches[33:320,])
```

#Localization Data
```{r}
PlotallTapCI(passive_localization, active_localization) 
```


#No-Cursor Data with the reach data and model output
```{r}
Reachmodelnc(nocursor_reaches, nocursor_nocursors, 'No-Cursor', color = colorNC)
Reachmodelnc(nocursorI_reaches, nocursorI_nocursors, 'No-Cursor', color = colorNNC)
Reachmodelnc(newnocursor_reaches, newnocursor_nocursors, 'No-Cursor', color = colorNC)
```

## Analysis of data
We begin with some ANOVA's and T-tests to check for significance

```{r, echo = FALSE}
### Create Data to use for ANOVA's and t-tests

ANOVAdata<- PrepdataforANOVA(active_reaches, passive_reaches, pause_reaches[33:320,], newnocursor_reaches[33:320,])
ANOVAPdata<- PrepdataforPropANOVA(active_localization,passive_localization)
TtestPdata<- PrepdataforPropT(active_localization, passive_localization)
Ttestdata<- PrepdataforT(active_reaches, passive_reaches, pause_reaches[33:320,], newnocursor_reaches[33:320,], newnocursor_nocursors)

```


```{r}
### Hand Localization Experiment
#reach data
FullHLANOVA<-ANOVAanalysis(ANOVAdata[ANOVAdata$Experiment == 'Active' | ANOVAdata$Experiment == 'Passive' | ANOVAdata$Experiment == 'Pause',])
FullHLANOVA
FullH1LANOVA<-ANOVAanalysis(ANOVAdata[ANOVAdata$Experiment == 'Active' | ANOVAdata$Experiment == 'Passive',])
FullH1LANOVA
FullH2LANOVA<-ANOVAanalysis(ANOVAdata[ANOVAdata$Experiment == 'Passive' | ANOVAdata$Experiment == 'Pause',])
FullH2LANOVA
FullH3LANOVA<-ANOVAanalysis(ANOVAdata[ANOVAdata$Experiment == 'Active' | ANOVAdata$Experiment == 'Pause',])
FullH3LANOVA
  IndependentT(Ttestdata, 'Active', 'Passive', 'Reach')
    IndependentT(Ttestdata, 'Active', 'Pause', 'Reach')
      IndependentT(Ttestdata, 'Pause', 'Passive', 'Reach')
#Proprioceptive data
FullPANOVA<-ANOVAanalysis(ANOVAPdata)
FullPANOVA
tpanalyzedata(TtestPdata)
PairedT(TtestPdata, 'Active', 'localization')
PairedT(TtestPdata, 'Passive', 'localization')


### Implicit Learning as the Slow Process Experiment
#Read Data
FullILANOVA<-ANOVAanalysis(ANOVAdata[ANOVAdata$Experiment == 'No-Cursor'  | ANOVAdata$Experiment == 'Pause',])
FullILANOVA
IndependentT(Ttestdata, 'Pause', 'No-Cursor', 'Reach')
PairedT(Ttestdata, 'No-Cursor', 'Reach')

#Reach Aftereffect Data
InitialLearning(Ttestdata, 'No-Cursor_No-Cursors', 'No-Cursors')
PairedT(Ttestdata, 'No-Cursor_No-Cursors', 'No-Cursors')

##Comparing 1st trial of no-cursors to 1st trial of prop.
propvsREA()


#Investigating Movement Times between the two groups of No-Cursors


plotmovetimes(dataset = uninstructed, dataset1 = Instructed)


RMunin<- NoCursorsTCombine(uninstructed)
RMin<- NoCursorsTCombine(Instructed)

RMunin$Experiment <- "Uninstructed"
RMin$Experiment <- "Instructed"
RM<- rbind(RMunin, RMin)

movementT(RM, "Uninstructed", "Instructed", "No-Cursors")
PairedMovementT(RM, "Instructed", "No-Cursors")
PairedMovementT(RM, "Uninstructed", "No-Cursors")


### Comparing Learning Rates Across Test Trials
      
FullANOVA<-ANOVAanalysis(ANOVAdata[ANOVAdata$Experiment == 'Active' | ANOVAdata$Experiment == 'Passive' | ANOVAdata$Experiment == 'No-Cursor' | ANOVAdata$Experiment == 'Pause',])
FullANOVA

### Polynomial Regressions
allpars<- ParticipantReachmodels2(active_reaches, passive_reaches, pause_reaches[33:320,], newnocursor_reaches[33:320,])
      pLogRegression(allpars)
```

```{r, echo = FALSE}
      
      
### Random Descriptive Stats
ActivePropMeans<- colMeans(TtestPdata[TtestPdata$Experiment == 'Active',1:ncol(TtestPdata)-1], na.rm = TRUE)
PassivePropMeans<- colMeans(TtestPdata[TtestPdata$Experiment == 'Passive',1:ncol(TtestPdata)-1], na.rm = TRUE)
NoCursorMeans<- colMeans(Ttestdata[Ttestdata$Experiment == 'No-Cursor',1:ncol(Ttestdata)-1], na.rm = TRUE)
NoCursorNCMeans<- colMeans(Ttestdata[Ttestdata$Experiment == 'No-Cursor_No-Cursors',1:ncol(Ttestdata)-1], na.rm = TRUE)
Allmeans<- Allmeans()
```
##MOdel comparison

Then we check to see if the data is more one-rate or two-rate on the group level
All of the data sets, when taken as a group, appear to be more two-rate than one rate. 
This makes sense since the size of the rebound is pretty large in at least the first 3 groups.
```{r}
Active_metrics<- GroupModelAICs(active_reaches, 'Active')
Passive_metrics<- GroupModelAICs(passive_reaches, 'Passive')
Pause_metrics<- GroupModelAICs(pause_reaches, 'Pause')
NC_metrics<- GroupModelAICs(newnocursor_reaches, 'No-Cursor', 'skewed')
metrics<- rbind(Active_metrics, Passive_metrics, Pause_metrics, NC_metrics)
groups = c('active', 'passive','pause', 'nocursor')
metrics$group<- groups


##model comparison for localization data to total, slow and prop
passivemetrics<-LocalizationModelCompare(passive_localization, passive_reaches, colorPA)
activemetrics<-LocalizationModelCompare(active_localization, active_reaches, colorA)

```

Figures for the manuscript
```{r real figures, echo = FALSE}
# 
# svglite(file='Fig 1.svg', width=12, height=8, system_fonts=list(sans = "Arial"))
# layout(matrix(c(1,2,3,4), nrow=2, byrow=TRUE), heights=c(2,2))
# Plotexp1CI(active_reaches, passive_reaches, pause_reaches[33:320,])
# PlotallTapCI(passive_localization, active_localization)
# Reachmodel(active_reaches, 'Active Localization', condition = 'loc', loc_data = active_localization, color=colorA)
# Reachmodel(passive_reaches, 'Passive Localization', condition = 'loc', loc_data = passive_localization, color=colorPA , yaxis = 'Hand Direction [°]')
# dev.off()
# 
# 
# svglite(file='Fig 2.svg', width=12, height=8, system_fonts=list(sans = "Arial"))
# layout(matrix(c(1,1,2,2,3,3,4,4,4,5,5,5), nrow=2, byrow=TRUE), heights=c(2,2))
# RegressionPLot3P()
# RegressionPLotchange()
# RegressionPLotec()
# plotfitPropModel(active_reaches, active_localization, colorA, 'Active Localizations')
# plotfitPropModel(passive_reaches, passive_localization, colorPA, 'Passive Localizations')
# dev.off()
# 
# 
# svglite(file='Fig 3.svg', width=12, height=4, system_fonts=list(sans = "Arial"))
# layout(matrix(c(1,2), nrow=1, byrow=TRUE), heights=c(2))
# Plotexp2CI(pause_reaches[33:320,],newnocursor_reaches[33:320,], pause_reaches[33:320,])
# Reachmodel(newnocursor_reaches, 'No-Cursor', grid = 'skewed', condition = 'nc', ncdata = newnocursor_nocursors, color = colorNC, yaxis = 'Hand Direction [°]')
# dev.off()
# 
# svglite(file='fig 5.svg', width=12, height=4, system_fonts=list(sans = "Arial"))
# Plotschedule(active_reaches)
# dev.off()


```
## Two-Rate model

In the two-rate model, the motor output X at trial t, $X_t$ is simply the added output of the slow and fast process at trial t:

<<<<<<< HEAD:TwoRateProprioception.Rmd
\begin{equation}
\label{tworate-total}
X_t = S_t + F_t
\end{equation}

The output of the slow process on the next trial (t+1) is determined by the error on the previous trial multiplied by a learning rate L, and the output on the previous trial multiplied by a retention rate R:

\begin{equation}
\label{tworate-slow}
S_{t+1} = (L^s \cdot E_t) + (R^s \cdot S_t)
\end{equation}

Similarly, the fast process has it's own learning rate and retention rate:

\begin{equation}
\label{tworate-fast}
F_{t+1} = (L^f \cdot E_t) + (R^f \cdot F_t)
\end{equation}
=======
[1] $X_t = S_t + F_t$ \label{tworate-total}

The output of the slow process on the next trial (t+1) is determined by the error on the previous trial multiplied by a learning rate L, and the output on the previous trial multiplied by a retention rate R:

[2] $S_{t+1} = L^s \cdot E_t + R^s \cdot S_t$ \label{tworate-slow}

Similarly, the fast process has it's own learning rate and retention rate:

[3] $F_{t+1} = L^f \cdot E_t + R^f \cdot F_t$ \label{tworate-fast}
