---
title: "Two Rate Proprioception Paper"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---
# Prepping Data

##Here we will make sure we have all the functions and scripts loaded we need

```{r eval=TRUE, echo=FALSE}
source('R/Analysis_Scripts.R')
source('R/Plots.R', encoding = 'UTF-8')
source('R/Repeated_Measures_Combine.R')
source('R/shared.R')
source('R/tworatemodel.R')
library('ez')
library('RateRate')
library('svglite')
library('effsize')
library('SMCL')
```

## We will now download and load the data and make the color scheme available
```{r eval=TRUE, echo=FALSE}
loadcolors()
downloadOSFdata()
loadalldata()
Allmeans<- Allmeans()
```

# Exploration of the data

##First we will look at each group of data and what each participant is doing
```{r}
PlotIndividualdata(pause_reaches[33:320,],3, "Individual Pause Data") #individual traces for pause data
PlotIndividualdata(active_reaches,1, "Individual Active Data")
PlotIndividualdata(passive_reaches,2, "Individual Passive Data")
PlotIndividualdata(nocursor_reaches[33:320,],4, "Individual No-Cursor Data")
PlotIndividualdata(nocursorI_reaches[33:320,],5, "Individual No-Cursor_I Data")
```
## Now we can look at the mean of each of the groups and of all the data we collected
```{r}
Allmeans[,c(1,4,7,10,16,19)]
```

# Training Trials
## Here we will look at how well the participants performed when the cursor was present
```{r}
PlotallreachesCI(active_reaches,passive_reaches, pause_reaches[33:320,],nocursor_reaches[33:320,],nocursorI_reaches[33:320,])
```
